\documentclass[11pt, a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{palatino}
\usepackage{microtype}
\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{float}
\usepackage{mdframed}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, backgrounds, calc}

% ── Colours ───────────────────────────────────────────────────────────────────
\definecolor{accent}{RGB}{30, 100, 60}
\definecolor{darkgreen}{RGB}{30, 100, 60}
\definecolor{lightgray}{RGB}{245, 245, 245}
\definecolor{midgray}{RGB}{130, 130, 130}
\definecolor{linkblue}{RGB}{20, 80, 160}
\definecolor{arrowgray}{RGB}{90, 90, 90}
\definecolor{colfield}{RGB}{215, 235, 255}
\definecolor{colingest}{RGB}{255, 243, 215}
\definecolor{colworker}{RGB}{220, 245, 230}
\definecolor{coldash}{RGB}{248, 230, 248}
\definecolor{colstore}{RGB}{255, 248, 215}
\definecolor{colretrain}{RGB}{255, 228, 228}
\definecolor{colreview}{RGB}{230, 230, 255}

\hypersetup{colorlinks=true,linkcolor=accent,urlcolor=linkblue,citecolor=accent,
  pdftitle={SLF Technical Report}}

\titleformat{\section}{\large\bfseries\color{accent}}{\thesection.}{0.6em}{}
  [\vspace{-4pt}\rule{\linewidth}{0.6pt}\vspace{2pt}]
\titleformat{\subsection}{\normalsize\bfseries\color{darkgreen}}{\thesubsection}{0.5em}{}

\pagestyle{fancy}\fancyhf{}
\fancyhead[L]{\small\textcolor{midgray}{SLF Trap Detector (PoC) --- Technical Report}}
\fancyhead[R]{\small\textcolor{midgray}{Pavle Subotic}}
\fancyfoot[C]{\small\textcolor{midgray}{\thepage}}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\headrule}{\hbox to\headwidth{%
  \color{midgray}\leaders\hrule height \headrulewidth\hfill}}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcommand{\code}[1]{\texttt{\small\color{darkgreen}#1}}

\newmdenv[backgroundcolor=lightgray,linecolor=accent,linewidth=2pt,
  leftline=true,rightline=false,topline=false,bottomline=false,
  innerleftmargin=10pt,innerrightmargin=10pt,
  innertopmargin=6pt,innerbottommargin=6pt,
  skipabove=8pt,skipbelow=8pt]{callout}

% ── TikZ styles ───────────────────────────────────────────────────────────────
\tikzset{
  sbox/.style 2 args={rectangle, rounded corners=4pt,
    draw=#1!70!black, fill=#1, text width=#2,
    minimum height=1.0cm, align=center, font=\small},
  sboxn/.style={rectangle, rounded corners=4pt,
    draw=midgray!70, fill=lightgray, text width=3.6cm,
    minimum height=0.85cm, align=center, font=\small},
  arr/.style={-{Stealth[length=5pt,width=4pt]}, thick, color=arrowgray},
  darr/.style={-{Stealth[length=5pt,width=4pt]}, thick, dashed, color=midgray},
  lbl/.style={font=\scriptsize\itshape, color=midgray, align=center},
}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}

% ── Title ─────────────────────────────────────────────────────────────────────
\begin{center}
{\LARGE\bfseries\color{accent}Technical Report:\\[4pt]
Spotted Lanternfly Detection\\[2pt]in Pheromone Trap Images}\\[14pt]
{\normalsize\textbf{Project:} SLF Trap Detector\quad
\textbf{Date:} March 2025\quad
\textbf{Author:} Pavle Suboti\'{c}\quad
\textbf{Version:} 3}\\[5pt]
\rule{\linewidth}{1pt}
\end{center}

\begin{callout}
\textbf{Abstract.}
We describe a proof-of-concept ML pipeline for detecting and counting adult
    \textit{Lycorma delicatula} a.k.a Spotted Lanternfly(SLF) in pheromone sticky trap
photographs. The challenge is to propose a model that has reasonable accuracy 
    with no labeled training dataset, and deployment on a CPU (no GPU). These restrictions 
    prevent the use of common state-of-the-art 
    techniques. We therefore utilize classical image processing
techniques. We combined a HOG\,+\,LBP\,+\,Random Forest classifier trained from synthetic
ground truth and achieves 85\,\% precision\,/\,77\,\% recall\,/\,81\,\% F1 with no
GPU and no manually labeled images. We conclude by a tentative design for a production
deployment architecture that incorporates a feedback loop that uses uncertain in-production
detections to continuously grow the training dataset with minimal expert effort.
\end{callout}

% ══════════════════════════════════════════════════════════════════════════════
\section{Problem Definition}

\subsection{Scope}
Detect and count adult \textit{Lycorma delicatula} in pheromone sticky trap
photographs. Framed as \textbf{object detection} (bounding boxes + confidence
scores) with a per-image count as the primary operational output. Instance
segmentation was considered and rejected as unnecessary at this stage; bounding
boxes are sufficient for counting and annotation bootstrapping.

\end{document}
